Pool Model - A unified Mathematical\\ Modelling Framework for Food Science

### 2025-11-01 paper/pool_model.tex
ensure that subcaptions have capital letters
update abm-ode comparisons

@@

    \begin{subfigure}[c]{0.5\columnwidth}
        \includegraphics[width=\columnwidth]{Figures-abm-homogenous-abm_ode_comparison.png}
        \subcaption{Hom. $D=30.0$\unit{\micro\metre\squared\per\minute}}
    \begin{subfigure}[c]{0.5\columnwidth}
        \includegraphics[width=\columnwidth]{Figures-abm-homogenous-low-diffusion-abm_ode_comparison.png}
        \subcaption{Hom. $D=5.0$\unit{\micro\metre\squared\per\minute}}
    \begin{subfigure}[c]{0.5\columnwidth}
        \includegraphics[width=\columnwidth]{Figures-abm-inhomogenous-abm_ode_comparison.png}%
        \subcaption{Het. $D=30.0$\unit{\micro\metre\squared\per\minute}}
    \begin{subfigure}[c]{0.5\columnwidth}
        \includegraphics[width=\columnwidth]{Figures-abm-random-abm_ode_comparison.png}%
        \subcaption{Rand. $D=30.0$\unit{\micro\metre\squared\per\minute}}
        Comparison of the \ac{ode} and \ac{abm} model for different configurations, showing
        homogenous (Hom.), heterogeneous (Het.) or randomized (Rand.) initial configurations.

>>>>

% Ensure that subcaptions have captial letter
\renewcommand{\thesubfigure}{\Alph{subfigure}}

@@

    \begin{tikzonimage}[width=0.5\columnwidth]
        {Figures-abm-homogenous-abm_ode_comparison.png}
        \node at (0, 1)[anchor=north west]{\textbf{A}};
    \begin{tikzonimage}[width=0.5\columnwidth]
        {Figures-abm-homogenous-low-diffusion-abm_ode_comparison.png}
        \node at (0, 1)[anchor=north west]{\textbf{B}};
    \begin{tikzonimage}[width=0.5\columnwidth]
        {Figures-abm-inhomogenous-abm_ode_comparison.png}
        \node at (0, 1)[anchor=north west]{\textbf{C}};
    \begin{tikzonimage}[width=0.5\columnwidth]
        {Figures-abm-random-abm_ode_comparison.png}
        \node at (0, 1)[anchor=north west]{\textbf{D}};
        (A-D) Comparison of the \ac{ode} and \ac{abm} model for different configurations, showing homogenous, heterogeneous or randomized initial configurations.
